Modeling and analyzing the Corona-virus warning app with the Isabelle Infrastructure framework

### 2020-07-02 paper.tex
added a shoert seciton on Motivcation to Intro

\TODO{Motivation: Why bother re-engineering a formal specification for a nicely developed privacy oriented app? physical aspects (adoption rate), formal proof etc}

>>>>

%{Motivation: Why bother re-engineering a formal specification for a nicely developed privacy oriented app? physical aspects (adoption rate), formal proof etc}
The technical advantage of modeling an application in the Isabelle Insider framework lies
in (a) having explicit representations of infrastructures, actors and policies in a
formal model that (b) allows additional automated verification of security properties
within the interactive theorem prover Isabelle.
Although the Corona-virus app hass been produced based on a sophisticated security
concept conceived by experts in the field, to our knowledge, no formal verification
has been involved.
